---
output:
  html_document

params:
  data: NA
  mapping: NA
  chart: NA
---


```{css, echo=FALSE}

.chart-md{
  padding: 0.5em 0.5em 0.2em 0.5em;
  background: #e7e7e7;
  margin-right: -15px;
  margin-left: -15px;
  margin-bottom: 15px;
  border: 1px solid #bbb;
}

.chart-md *{
  display:inline-block;
  padding-left:0.4em;
}

.chart-md strong{
  font-size:1.2em;
}

.chart-md small{
  font-size:0.8em;
  color:#999;
}

.chart-md .chart-link{
  padding-right:0.5em;
}
```

```{r results='asis', echo = FALSE, message=FALSE, warning = FALSE}
library(safetyGraphics)
library(yaml)

mapping <- params$mapping
data <- params$data
chart<-params$chart

header <- makeChartSummary(chart, class="chart-md")
chart_params <- makeChartParams(data, chart, mapping)

mapping_list<-generateMappingList(mapping %>% filter(domain %in% chart$domain))
if(length(mapping_list)==1){
  mapping_list <- mapping_list[[1]]
}

```
## {safetyGraphics}: `r params$chart$label` report {.tabset .tabset-fade} 
### `r params$chart$label`

`r header`

```{r  fig.height=7, fig.width=9, echo=FALSE, message=FALSE, warning=FALSE}
  do.call(chart$functions$main, chart_params)
```  

### Code 

This chart can be re-run using the code below after updating to load your data. 

#### Chart Code 

```
`r paste(makeChartExport(chart, mapping_list),collapse="\n")`
```

### Background
This chart was generataed using the safetyGraphics shiny app. The safetyGraphics package provides a framework for evaluation of clinical trial safety in R. Examples and additional documentation are available [here](https://github.com/ASA-DIA-InteractiveSafetyGraphics/safetyGraphics). 

